### 2015-07-06 2015-compmorphon-morphver/poster.tex
more work on Tuvan velar elision
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61175 72bbbca6-d526-0410-a7d9-f06f51895060

					- Anderson and Harrison (1999, pp.\ 9, 22-23)\\
					\includegraphics[width=0.49\textwidth]{img/andersonharrison9}\\
					\includegraphics[width=0.49\textwidth]{img/andersonharrison22-23}\\
					- Исхаков, Ф.Г.; Пальмбах (1961, pp.\ 117-118)\\
					\includegraphics[width=0.49\textwidth]{img/isxakovpalmbax117}\\

@@

			\htwo{More complete characterisation}

			\includegraphics[width=0.4\textwidth]{img/andersonharrison35}\\

>>>>

					\begin{itemize}
						\item Anderson and Harrison (1999, pp.\ 9, 22-23)
					\end{itemize}
					\includegraphics[width=0.49\textwidth]{img/andersonharrison9}\\
					\includegraphics[width=0.49\textwidth]{img/andersonharrison22-23}
					\begin{itemize}
						\item Исхаков, Ф.Г.; Пальмбах (1961, pp.\ 117-118)
					\end{itemize}
					\includegraphics[width=0.49\textwidth]{img/isxakovpalmbax117}

				\htwo{More complete characterisation}
				\begin{itemize}
					\item /k/ ‹к› elides at the end of ≥1-{\qipa 𝛔} stems intervocalically;
					\item /g/ ‹г› elides at the end of any stem intervocalically;
					\item /ŋ/ ‹ң› elides at the end of \textit{some} stems intervocalically.
				\end{itemize}
				examples of correct forms in grammars:\\
				\includegraphics[width=0.2\textwidth]{img/andersonharrison35}

@@
